All Your Graphs Belong to Us

### 2012-07-11 doc/asplos13/grappa.tex
communication v0

>>>>

With Grappa, from the perspective of the application, all communication between tasks occurs through global shared memory.  These requests are ultimately translated into explicit inter system node communication requests that are dispatched to GASnet.  Under the hood there exists a key component within Grappa, the message aggregator, that makes fine-grained communication efficient on commodity Infiniband networks.  Infiniband achieves its peek bisection bandwidth \emph{only} when the packet sizes are relatively large (a kilobyte or more).  In our experience, graph algorithms request objects through the caching system (previously described) with a median object size of \checkme{16} bytes.  Our measurements, confirm manufactures published data~\cite{infinibandbandwidth}, that with this packet size the bisection bandwidth is only a small fraction, less than ~\checkme{5\%} of the peak bisection bandwidth.  The reason for this discrepancy is the combination of overheads associated with handling each packet (in terms of bytes that form the actual Infiniband packet, processing time at the card and processing on the CPU within the driver stack).

To work around this problem we perform packet aggregation.  Instead of dispatching a packet immediately to the Infiniband hardware, Grappa holds onto an individual communication request.  Pending requests that are to be sent to the same remote node are queued.  Once a sufficient number of them (in terms of bytes) or a timeout occurs, they are dispatched as a single packet to GASnet and onward to the Infiniband network.  In Section~\ref{sec:results} we explore the sensitivity of performance to these two key parameters, but the net result is that performance is maximized by aiming to aggregate for \checkme{1024} bytes and \checkme{1ms}.
